\Large \bf CS380S: Project Proposal

### 2018-09-16 proposal/proposal.tex
Created another TODO task
Filled in research hypothesis with motivating examples
Updated based on facebook conversation

@@

@@

\begin{enumerate}
	\item Debian/OpenSSL Bug 
		\begin{enumerate}
			\item \url{https://www.schneier.com/blog/archives/2008/05/random_number_b.html}
			\item \url{https://research.swtch.com/openssl}
			\item \url{https://freedom-to-tinker.com/2013/09/20/software-transparency-debian-openssl-bug/}
			\item \url{https://www.cs.umd.edu/class/fall2017/cmsc818O/papers/private-keys-public.pdf}
		\end{enumerate}
	\item Data flow
		\begin{enumerate}
			\item \url{https://en.wikipedia.org/wiki/Data-flow_analysis}
			\item \url{https://www.seas.harvard.edu/courses/cs252/2011sp/slides/Lec02-Dataflow.pdf}
		\end{enumerate}
\end{enumerate}

\subsection{Related Research}

>>>>

\begin{enumerate}
	\item Determine data dependency tool (for C/C++) to use, conduct background research (\textit{2 weeks})
	\item Adapt tool to identify the OpenSSL bug (\textit{6 weeks})
	\item Test on other cases like bitcoin wallets (\textit{2 weeks})
	\item Prepare presentation/writeup (\textit{1 week})
	\item Integrate tool into compiler toolchain like clang (\textit{optional})
\end{enumerate}

@@

\begin{enumerate}
	\item An automated tool can detect entropy bugs in real-world programs.
	\item Entropy is insufficiently propagated in programs that rely on cryptography.
\end{enumerate}

@@

\begin{enumerate}
	\item Debian/OpenSSL Bug 
		\begin{enumerate}
			\item \url{https://www.schneier.com/blog/archives/2008/05/random_number_b.html}
			\item \url{https://research.swtch.com/openssl}
			\item \url{https://freedom-to-tinker.com/2013/09/20/software-transparency-debian-openssl-bug/}
			\item \url{https://www.cs.umd.edu/class/fall2017/cmsc818O/papers/private-keys-public.pdf}
		\end{enumerate}
	\item Data flow
		\begin{enumerate}
			\item \url{https://en.wikipedia.org/wiki/Data-flow_analysis}
			\item \url{https://www.seas.harvard.edu/courses/cs252/2011sp/slides/Lec02-Dataflow.pdf}
		\end{enumerate}

	% TODO maybe have a section about cryptocurrency wallets, etc.
\end{enumerate}

\subsection{Related research}
